Wrinkling of a confined porous layer

### 2014-12-09 fig_plis/article_plis.tex
Move figures around to have them in front of the corresponding text. Bibliography

\documentclass[twocolumn,superscriptaddress,showpacs,preprintnumbers,amsmath,amssymb,prl]{revtex4-1}
\usepackage[utf8]{inputenc}

@@

@@

The slow acidification of a protein (sodium caseinate) solution up to the isoelectric pH induces gelation. Since caseins adsorb strongly to interfaces, the resulting gel sticks to container walls, allowing rheological measurements. As shown in Fig.~\ref{fig:acidification}, further decrease of the pH beyond the isoeletric point weakens the gel. This non monotonous behaviour of the elastic modulus translates in a non monotonous mesh size in a microscopy cell (slit geometry) coated so that the casein could not adsorb on the top wall (Fig.~\ref{fig:acidification}c), i.e. in syn\ae{}resis (solvent expulsion) followed by swelling.

@@

\bibliographystyle{naturemag3}

@@

\begin{figure}
	\includegraphics{acidification}
	\caption{Acid-induced protein gels properties behave non-monotonously with pH. (a) pH decrease in 4\%w sodium caseinate solution acidified by 4\%w GDL. Horizontal line indicates isoelectric pH of casen (b) Evolution of storage modulus measured in a rheometer (full adhesion to rotor and stator). (c) Evolution of pore size measured by confocal microscopy in a half coated microscopy cell (no adhesion to cell ceiling, syn\ae{}resis and swelling allowed).}
	\label{fig:acidification}
\end{figure}

>>>>

\documentclass[twocolumn,superscriptaddress,showpacs,preprintnumbers,
amsmath,amssymb,prl]{revtex4-1}
\usepackage[utf8]{inputenc}

@@

\section*{Introduction}

\clearpage
\newpage

@@

\begin{figure}[b]
	\includegraphics{acidification}
	\caption{Acid-induced protein gels properties behave non-monotonously with pH. (a) pH decrease in 4\%w sodium caseinate solution acidified by 4\%w GDL. Horizontal line indicates isoelectric pH of casen (b) Evolution of storage modulus measured in a rheometer (full adhesion to rotor and stator). (c) Evolution of pore size measured by confocal microscopy in a half coated microscopy cell (no adhesion to cell ceiling, syn\ae{}resis and swelling allowed).}
	\label{fig:acidification}
\end{figure}

The slow acidification of a protein (sodium caseinate) solution down to the isoelectric pH induces gelation. Since caseins adsorb strongly to interfaces, the resulting gel sticks to container walls, allowing rheological measurements (see Fig.~\ref{fig:acidification}b). Further decrease of the pH beyond the isoeletric point weakens the gel. This non monotonous behaviour of the elastic modulus translates in a non monotonous mesh size in a microscopy cell (slit geometry) coated so that the casein could not adsorb on the top wall (Fig.~\ref{fig:acidification}c), i.e. in syn\ae{}resis (solvent expulsion) followed by swelling.

@@

\bibliographystyle{naturemag3}
\bibliography{Yaourt}

@@
